Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-06-01 doc/manuscript/manuscript.Rmd
saved manuscript

## Yield contrasts
Several RILs in each of the tests had yield that was comparable to that of their check cultivars. This was determined both quanititatively through the use of contrasts between the mean of each RIL with the average of the yield check means, and qualitatively by inspecting the standard errors on the estimation of the genotype marginal means for yield. No genotypes had yield that was quantitatively higher than that of the yield checks, however many had comparable yield. Many of these genotypes with comparable yield also had protein content that was superior to the check average in each test. No genotypes had oil that was superior to the check cultivars, but some had comparable yield and oil content as well as superior protein content.

RILs were also evaluated for lodging and seed quality. All RILs had seed quality that was on par with that of the high-yielding checks however, however 11 genotypes had lodging scores that were significantly greater than the checks on the basis of contrasts. These RILs were removed from consideration for recommendation on the basis of their relatively poor agronomic performance.

@@

From among these lines, only

@@

>>>>

## Yield contrasts
Several RILs in each of the tests had yield that was comparable to that of their check cultivars. This was determined both quantitatively through the use of contrasts between the mean of each RIL with the average of the yield check means, and qualitatively by inspecting the standard errors on the estimation of the genotype marginal means for yield. No genotypes had yield that was quantitatively higher than that of the yield checks, however many had comparable yield. Many of these genotypes with comparable yield also had protein content that was superior to the check average in each test. No genotypes had oil that was superior to the check cultivars, but some had comparable yield and oil content as well as superior protein content.

RILs were also evaluated for lodging and seed quality. All RILs had seed quality that was on par with that of the high-yielding checks however, however 11 genotypes had lodging scores that were statistically significantly greater than the checks on the basis of contrasts. These RILs were removed from consideration for recommendation on the basis of their relatively poor agronomic performance.

@@

A strong negative correlation was observed in both populations betweeen seed oil and seed protein. This observation matches well with previous findings on the inverse correlation between seed protein and seed oil. Many RILs had high protein when compared with the check cultivars so it was not surprising that relatively few had both a superior seed protein content, and a comparable seed oil content.

@@

Among these genotypes are several with both average seed protein and average seed yield that were greater than the averages of the checks for each test. These N18-1632-1, N18-1620, N18-1635 from test 1 and RILs N18-1761 and N18-1627 from test 2. Of particular note are genotypes N18-1632-1 from test 1 and N18-1761 from test 2. On average, genotype N18-1632-1 had a protein content that was 113.9% of the check average while maintaining a yield average that was 101.5% that of the check average. SImilarly, RIL N18-1761 from test 2 had a protein
